XXXXX

### 2014-09-27 paper/paper1.tex
R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS

@@

@@

@@

@@

@@

\begin{table}
\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
\label{tab:RequirementsNotCoveredOWL2QL-1}
\centering
\begin{tabular}{ll}
\hr
Requirements & Covering Constraint Languages \\
\hr
R-6-EQUIVALENT-INDIVIDUALS (SameIndividual) & OWL 2 DL \\
R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS (DisjointUnion) & OWL 2 DL \\
R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC & ShEx \\
R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC & ShEx \\
R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS (ObjectIntersectionOf) & OWL 2 DL \\
R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) & OWL 2 DL \\
R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (DisjointUnionOf) & OWL 2 DL \\
R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) & OWL 2 DL \\
R-19-NEGATION-OF-CLASS-EXPRESSIONS (ObjectComplementOf) & OWL 2 DL \\
R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) & OWL 2 DL \\
R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS & SPIN \\
R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPIN, ShEx \\
R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPIN, ShEx \\
R-24-PROVENANCE-CONSTRAINTS & \\
R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS & SPIN, RS \\
R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS (ObjectOneOf) & OWL 2 DL \\
R-31-DEFAULT-VALUES-OF-RDF-OBJECTS & SPIN, BF, RS \\
R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
R-33-NEGATIVE-OBJECT-CONSTRAINTS \\
R-34-AVAILABLE-CLASS-DEFINITION & ShEx, SPIN \\
R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS & ShEx, BF, SPIN \\
R-37-ALLOWED-VALUES-FOR-RDF-LITERALS (DataOneOf) & OWL 2 DL \\
R-38-DEFAULT-VALUES-OF-RDF-LITERALS & SPIN, BF, RS \\
R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
R-44-PATTERN-MATCHING-ON-RDF-LITERALS & ShEx, RS, SPIN \\
R-41-STATISTICAL-COMPUTATIONS & SPIN \\
R-42-COMPUTATIONS-BASED-ON-DATATYPE & \\
R-43-COMPARISONS-BASED-ON-DATATYPE & DQTP, ShEx, SPIN \\
R-45-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
R-46-CONSTRAINING-FACETS & Stardog, SPIN \\
R-47-LANGUAGE-TAG-MATCHING & SPIN \\
R-48-MISSING-LANGUAGE-TAGS & SPIN \\
R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG & DQTP, SPIN \\
R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS & SPIN \\
R-51-HTML-HANDLING-OF-RDF-LITERALS & SPIN \\
R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
R-55-OBJECT-PROPERTY-PATHS (SubObjectPropertyOf) & OWL 2 DL \\
R-57-FUNCTIONAL-OBJECT-PROPERTIES (FunctionalObjectProperty) & OWL 2 DL \\
R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES (InverseFunctionalObjectProperty) & OWL 2 DL \\
R-63-TRANSITIVE-OBJECT-PROPERTIES (TransitiveObjectProperty) & OWL 2 DL \\
R-65-FUNCTIONAL-DATA-PROPERTIES (FunctionalDataProperty) & OWL 2 DL \\
R-66-PROPERTY-GROUPS & ShEx, SPIN \\
R-67-CLASSIFY-PROPERTIES-ACCORDING-TO-OCCURRENCE & \\
R-68-REQUIRED-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
R-69-OPTIONAL-PROPERTIES  (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
R-70-REPEATABLE-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
R-71-CONDITIONAL-PROPERTIES \\
R-72-RECOMMENDED-PROPERTIES \\
\hr
\end{tabular}
\end{table}

@@

\begin{table}
\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
\label{tab:RequirementsNotCoveredOWL2QL-3}
\centering
\begin{tabular}{ll}
\hr
Requirements & Covering Constraint Languages \\
\hr
R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) & OWL 2 DL \\
R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) & OWL 2 DL \\
R-98-CHECK-VALIDITY-OF-URIS & \\
R-106-EXTENSIBLE-CONSTRAINT-LANGUAGE & \\
R-112-EXTENSIBLE-CONSTRAINTS & \\
R-114-PROVIDE-RDF-REST-SERVICES-FOR-RDF-VALIDATION & \\
R-119-VALIDATION-ON-NAMED-GRAPHS & \\
R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
R-121-SPECIFY-ORDER-OF-RDF-RESOURCES & \\
R-123-STATE & \\
R-125-RDF-SHAPE-CHECKING & ShEx \\
R-126-CUSTOMIZABLE-VALIDATION-PROCESS & \\
R-134-SPECIFY-USAGE-OF-TERMS & \\
R-135-CONSTRAINT-LEVELS & \\
R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, SPIN \\
R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
R-146-CONSTRAINT-VALIDATION-OF-RDF-INPUT-WITH-RESPECT-TO-EXISTING-RDF & \\
R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS & SPIN, DQTP \\
R-151-USEFUL-MESSAGE-VALIDATION-RESULTS & SPIN, DQTP, ShEx, Pellet \\
R-152-FIND-NOT-VALIDATED-TRIPLES & ShEx \\
R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS & SPIN \\
R-154-HANDLE-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA & ShEx, SPIN \\
R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS & SPIN \\
R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS & SPIN \\
R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS & SPIN, ShEx, Stardog, Pellet \\
R-166-RDF-STREAMING-VALIDATION & \\
R-167-VALIDATE-RDF-IN-AN-HTML-DOCUMENT-CONSTAINING-RDFA-MARKUP & \\
R-170-VALIDATION-OF-SPARQL-ENDPOINTS & \\
R-171-VALIDATION-OF-URIS-BY-DEREFERENCING & \\
R-172-GENERATE-HUMAN-READABLE-DOCUMENTATION & \\
R-176-PROVIDE-HIGH-LEVEL-VOCABULARY-FOR-THE-MOST-COMMON-TYPES-OF-CONSTRAINTS & \\
R-179-ASSOCIATE-CONSTRAINTS-WITH-RDF-DOCUMENTS & \\
R-180-ASSOCIATE-CONSTRAINTS-WITH-RDF-DATASETS & \\
R-181-ASSOCIATE-CONSTRAINTS-WITH-RDF-REST-APIS & \\
R-183-CONSTRAINTS-ABOUT-CONSTRAINTS & \\
R-185-FEDERALIZED-RDF-VALIDATION & \\
R-186-EXTEND-EXPRESSIVITY-WITH-SPARQL & \\
R-188-EXPRESSIVITY-OF-CONSTRAINT-LANGUAGE-EQUIVALENT-TO-SPARQL & \\
R-189-ADD-ANNOTATIONS-TO-CONSTRAINT-VIOLATION-OBJECTS & \\
R-191-SHAPES-RELATED-TO-TYPES & \\
R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS & \\
R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS & SPIN \\
\hr
\end{tabular}
\end{table}

>>>>

\begin{itemize}
	\item see R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC
\end{itemize}

@@

Covering approaches:

DQTP (MATCH Pattern), OWL 2 DL, RS, ShEx, SPARQL, SPIN

@@

\begin{ex}

\end{ex}

@@

\subsubsection{R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS}

Covering approaches: DQTP (MATCH Pattern), OWL 2 DL, SPARQL, SPIN

MATCH Pattern \cite{Kontokostas2014}

Application logic or real world constraints may put restrictions on the form of a literal value.
P1 is the property we need to check against REGEX and
NOP can be a not operator (!) or empty.

\begin{ex}
SELECT DISTINCT ?s WHERE { ?s %%P1%% ?value .
    FILTER ( %%NOP%% regex(str(?value), %%REGEX%) ) }
\end{ex}

example test bindings (DQTP):

\begin{ex}
1. dbo:isbn format is different ’!’ from '^([iIsSbBnN 0-9-])*$'
2. dbo:postCode format is different ‘!’ from 'ˆ[0-9]{5}$'
3. foaf:phone contains any letters ('[A-Za-z]')
\end{ex}

\begin{ex}
dbo:isbn format is different ’!’ from '^([iIsSbBnN 0-9-])*$'

P1 => dbo:isbn
NOP => !
REGEX => 'ˆ([iIsSbBnN 0-9-])*$'
\end{ex}

\begin{ex}
:FoundationsOfSWTechnologies
    dbo:isbn 'ISBN-13 978-1420090505' .
\end{ex}

\begin{ex}
:HandbookOfSWTechnologies
    dbo:isbn 'DOI 10.1007/978-3-540-92913-0' .
\end{ex}

@@

XSD constraining facets: \url{http://www.w3.org/TR/2001/REC-xmlschema-2-20010502/#rf-facets}

@@

\begin{table}
\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
\label{tab:RequirementsNotCoveredOWL2QL-1}
\centering
\begin{tabular}{ll}
\hr
Requirements & Covering Constraint Languages \\
\hr
R-6-EQUIVALENT-INDIVIDUALS (SameIndividual) & OWL 2 DL \\
R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS (DisjointUnion) & OWL 2 DL \\
R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC & ShEx \\
R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC & ShEx \\
R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS (ObjectIntersectionOf) & OWL 2 DL \\
R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) & OWL 2 DL \\
R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (DisjointUnionOf) & OWL 2 DL \\
R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) & OWL 2 DL \\
R-19-NEGATION-OF-CLASS-EXPRESSIONS (ObjectComplementOf) & OWL 2 DL \\
R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) & OWL 2 DL \\
R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS & SPIN \\
R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPIN, ShEx \\
R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPIN, ShEx \\
R-24-PROVENANCE-CONSTRAINTS & \\
R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS & SPIN, RS \\
R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS (ObjectOneOf) & OWL 2 DL \\
R-31-DEFAULT-VALUES-OF-RDF-OBJECTS & SPIN, BF, RS \\
R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
R-33-NEGATIVE-OBJECT-CONSTRAINTS \\
R-34-AVAILABLE-CLASS-DEFINITION & ShEx, SPIN \\
R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS & ShEx, BF, SPIN \\
R-37-ALLOWED-VALUES-FOR-RDF-LITERALS (DataOneOf) & OWL 2 DL \\
R-38-DEFAULT-VALUES-OF-RDF-LITERALS & SPIN, BF, RS \\
R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
R-44-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, ShEx, RS, SPARQL, SPIN \\
R-41-STATISTICAL-COMPUTATIONS & SPIN \\
R-42-COMPUTATIONS-BASED-ON-DATATYPE & \\
R-43-COMPARISONS-BASED-ON-DATATYPE & DQTP, ShEx, SPIN \\
R-45-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
R-46-CONSTRAINING-FACETS & Stardog, SPIN \\
R-47-LANGUAGE-TAG-MATCHING & SPIN \\
R-48-MISSING-LANGUAGE-TAGS & SPIN \\
R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG & DQTP, SPIN \\
R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS & SPIN \\
R-51-HTML-HANDLING-OF-RDF-LITERALS & SPIN \\
R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
R-55-OBJECT-PROPERTY-PATHS (SubObjectPropertyOf) & OWL 2 DL \\
R-57-FUNCTIONAL-OBJECT-PROPERTIES (FunctionalObjectProperty) & OWL 2 DL \\
R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES (InverseFunctionalObjectProperty) & OWL 2 DL \\
R-63-TRANSITIVE-OBJECT-PROPERTIES (TransitiveObjectProperty) & OWL 2 DL \\
R-65-FUNCTIONAL-DATA-PROPERTIES (FunctionalDataProperty) & OWL 2 DL \\
R-66-PROPERTY-GROUPS & ShEx, SPIN \\
R-67-CLASSIFY-PROPERTIES-ACCORDING-TO-OCCURRENCE & \\
R-68-REQUIRED-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
R-69-OPTIONAL-PROPERTIES  (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
R-70-REPEATABLE-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
R-71-CONDITIONAL-PROPERTIES \\
R-72-RECOMMENDED-PROPERTIES \\
\hr
\end{tabular}
\end{table}

@@

\begin{table}
\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
\label{tab:RequirementsNotCoveredOWL2QL-3}
\centering
\begin{tabular}{ll}
\hr
Requirements & Covering Constraint Languages \\
\hr
R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) & OWL 2 DL \\
R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) & OWL 2 DL \\
R-98-CHECK-VALIDITY-OF-URIS & \\
R-106-EXTENSIBLE-CONSTRAINT-LANGUAGE & \\
R-112-EXTENSIBLE-CONSTRAINTS & \\
R-114-PROVIDE-RDF-REST-SERVICES-FOR-RDF-VALIDATION & \\
R-119-VALIDATION-ON-NAMED-GRAPHS & \\
R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
R-121-SPECIFY-ORDER-OF-RDF-RESOURCES & \\
R-123-STATE & \\
R-125-RDF-SHAPE-CHECKING & ShEx \\
R-126-CUSTOMIZABLE-VALIDATION-PROCESS & \\
R-134-SPECIFY-USAGE-OF-TERMS & \\
R-135-CONSTRAINT-LEVELS & \\
R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, SPARQL, SPIN \\
R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
R-146-CONSTRAINT-VALIDATION-OF-RDF-INPUT-WITH-RESPECT-TO-EXISTING-RDF & \\
R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS & SPIN, DQTP \\
R-151-USEFUL-MESSAGE-VALIDATION-RESULTS & SPIN, DQTP, ShEx, Pellet \\
R-152-FIND-NOT-VALIDATED-TRIPLES & ShEx \\
R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS & SPIN \\
R-154-HANDLE-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA & ShEx, SPIN \\
R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS & SPIN \\
R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS & SPIN \\
R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS & SPIN, ShEx, Stardog, Pellet \\
R-166-RDF-STREAMING-VALIDATION & \\
R-167-VALIDATE-RDF-IN-AN-HTML-DOCUMENT-CONSTAINING-RDFA-MARKUP & \\
R-170-VALIDATION-OF-SPARQL-ENDPOINTS & \\
R-171-VALIDATION-OF-URIS-BY-DEREFERENCING & \\
R-172-GENERATE-HUMAN-READABLE-DOCUMENTATION & \\
R-176-PROVIDE-HIGH-LEVEL-VOCABULARY-FOR-THE-MOST-COMMON-TYPES-OF-CONSTRAINTS & \\
R-179-ASSOCIATE-CONSTRAINTS-WITH-RDF-DOCUMENTS & \\
R-180-ASSOCIATE-CONSTRAINTS-WITH-RDF-DATASETS & \\
R-181-ASSOCIATE-CONSTRAINTS-WITH-RDF-REST-APIS & \\
R-183-CONSTRAINTS-ABOUT-CONSTRAINTS & \\
R-185-FEDERALIZED-RDF-VALIDATION & \\
R-186-EXTEND-EXPRESSIVITY-WITH-SPARQL & \\
R-188-EXPRESSIVITY-OF-CONSTRAINT-LANGUAGE-EQUIVALENT-TO-SPARQL & \\
R-189-ADD-ANNOTATIONS-TO-CONSTRAINT-VIOLATION-OBJECTS & \\
R-191-SHAPES-RELATED-TO-TYPES & \\
R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS & \\
R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS & SPIN \\
\hr
\end{tabular}
\end{table}
